XXXXX

### 2014-09-25 paper/paper1.tex
R-160 - R-182

evaluation using practical data set

@@

\begin{itemize}
	\item existential quantification to a class expression or a data range (ObjectSomeValuesFrom and DataSomeValuesFrom) in the subclass position
  \item self-restriction (ObjectHasSelf)
  \item existential quantification to an individual or a literal (ObjectHasValue, DataHasValue)
  \item enumeration of individuals and literals (ObjectOneOf, DataOneOf)
  \item universal quantification to a class expression or a data range (ObjectAllValuesFrom, DataAllValuesFrom)
  \item cardinality restrictions (ObjectMaxCardinality, ObjectMinCardinality, ObjectExactCardinality, DataMaxCardinality, DataMinCardinality, DataExactCardinality)
  \item disjunction (ObjectUnionOf, DisjointUnion, and DataUnionOf)
  \item property inclusions (SubObjectPropertyOf) involving property chains
  \item functional and inverse-functional properties (FunctionalObjectProperty, InverseFunctionalObjectProperty, and FunctionalDataProperty)
  \item transitive properties (TransitiveObjectProperty)
  \item keys (HasKey)
  \item individual equality assertions and negative property assertions
\end{itemize}

\begin{table}
\caption{RDF Validation Requirements Covered by OWL 2 QL}
\label{tab:RequirementsCoveredOWL2QL}
\centering
\begin{tabular}{ll}
\hr
Requirements Classification & Requirements \\
\hr
& R-1-UNIQUENESS-OF-URIS \\
& R-2-UNIQUE-INSTANCES \\
& R-3-EQUIVALENT-CLASSES (EquivalentClasses) \\
& R-4-EQUIVALENT-OBJECT-PROPERTIES (EquivalentObjectProperties) \\
& R-5-EQUIVALENT-DATA-PROPERTIES (EquivalentDataProperties) \\
& R-7-DISJOINT-CLASSES (DisjointClasses) \\
& R-9-DISJOINT-OBJECT-PROPERTIES (DisjointObjectProperties) \\
& R-10-DISJOINT-DATA-PROPERTIES (DisjointDataProperties) \\
& R-14-DISJOINT-INDIVIDUALS (DifferentIndividuals) \\
& R-25-OBJECT-PROPERTY-DOMAIN (ObjectPropertyDomain) \\
& R-26-DATA-PROPERTY-DOMAIN (DataPropertyDomain) \\
& R-27-CLASS-SPECIFIC-VALIDATION \\
& R-28-OBJECT-PROPERTY-RANGE (ObjectPropertyRange) \\
& R-35-DATA-PROPERTY-RANGE (DataPropertyRange) \\
& R-54-SUB-OBJECT-PROPERTIES (SubObjectPropertyOf) \\
& R-56-INVERSE-OBJECT-PROPERTIES (ObjectInverseOf) \\
& R-59-REFLEXIVE-OBJECT-PROPERTIES (ReflexiveObjectProperty) \\
& R-60-IRREFLEXIVE-OBJECT-PROPERTIES (IrreflexiveObjectProperty) \\
& R-61-SYMMETRIC-OBJECT-PROPERTIES (SymmetricObjectProperty) \\
& R-62-ASYMMETRIC-OBJECT-PROPERTIES (AsymmetricObjectProperty) \\
& R-64-SUB-DATA-PROPERTIES (SubDataPropertyOf) \\
\hr
\end{tabular}
\end{table}

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL-3}
\centering
\begin{tabular}{ll}
\hr
Requirements & Covering Constraint Languages \\
\hr
R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\

R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
\hr
\end{tabular}
\end{table}

>>>>

\subsection{Evaluation Using Practical Data Set}

Table~\ref{tab:RequirementsCoveredOWL2QL}

\begin{table}
\caption{RDF Validation Requirements Covered by OWL 2 QL}
\label{tab:RequirementsCoveredOWL2QL}
\centering
\begin{tabular}{ll}
\hr
Requirements Classification & Requirements \\
\hr
& R-1-UNIQUENESS-OF-URIS \\
& R-2-UNIQUE-INSTANCES \\
& R-3-EQUIVALENT-CLASSES (EquivalentClasses) \\
& R-4-EQUIVALENT-OBJECT-PROPERTIES (EquivalentObjectProperties) \\
& R-5-EQUIVALENT-DATA-PROPERTIES (EquivalentDataProperties) \\
& R-7-DISJOINT-CLASSES (DisjointClasses) \\
& R-9-DISJOINT-OBJECT-PROPERTIES (DisjointObjectProperties) \\
& R-10-DISJOINT-DATA-PROPERTIES (DisjointDataProperties) \\
& R-14-DISJOINT-INDIVIDUALS (DifferentIndividuals) \\
& R-25-OBJECT-PROPERTY-DOMAIN (ObjectPropertyDomain) \\
& R-26-DATA-PROPERTY-DOMAIN (DataPropertyDomain) \\
& R-27-CLASS-SPECIFIC-VALIDATION \\
& R-28-OBJECT-PROPERTY-RANGE (ObjectPropertyRange) \\
& R-35-DATA-PROPERTY-RANGE (DataPropertyRange) \\
& R-54-SUB-OBJECT-PROPERTIES (SubObjectPropertyOf) \\
& R-56-INVERSE-OBJECT-PROPERTIES (ObjectInverseOf) \\
& R-59-REFLEXIVE-OBJECT-PROPERTIES (ReflexiveObjectProperty) \\
& R-60-IRREFLEXIVE-OBJECT-PROPERTIES (IrreflexiveObjectProperty) \\
& R-61-SYMMETRIC-OBJECT-PROPERTIES (SymmetricObjectProperty) \\
& R-62-ASYMMETRIC-OBJECT-PROPERTIES (AsymmetricObjectProperty) \\
& R-64-SUB-DATA-PROPERTIES (SubDataPropertyOf) \\
& R-93-DIFFERENCE-BETWEEN-CONSTRAINTS-ON-OBJECT-AND-DATA-PROPERTIES \\
& R-94-POSITIVE-OBJECT-PROPERTY-ASSERTIONS (ObjectPropertyAssertion) \\
& R-95-POSITIVE-DATA-PROPERTY-ASSERTIONS (DataPropertyAssertion) \\
& R-99-STABLE-IDENTIFICATION-OF-CONSTRAINTS \\
& R-100-SUBSUMPTION (SubClassOf) \\
& R-101-DECLARATIVE-CONSTRAINT-LANGUAGE \\
& R-102-INTUITIVE-CONSTRAINT-LANGUAGE \\
& R-103-HIGH-LEVEL-CONSTRAINT-LANGUAGE \\
& R-104-CONSTRAINT-LANGUAGE-HAVING-IMPLEMENTATION-LANGUAGE \\
& R-105-CONSTRAINT-LANGUAGE-TRANSLATABLE-TO-IMPLEMENTATION-LANGUAGE \\
& R-107-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-UML \\
& R-108-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-XML-SCHEMA \\
& R-109-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-OCL \\
& R-110-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-SPARQL \\
\hr
\end{tabular}
\end{table}

\begin{table}
\caption{RDF Validation Requirements Covered by OWL 2 QL}
\label{tab:RequirementsCoveredOWL2QL}
\centering
\begin{tabular}{ll}
\hr
Requirements Classification & Requirements \\
\hr
& R-111-BASIC-USE-CASES-COVERED-BY-CONSTRAINT-LANGUAGE \\
& R-113-INTERACTION-OF-VALIDATION-WITH-REASONING \\
& R-115-CLOSED-WORLD-ASSUMPTION-CWA \\
& R-116-UNIQUE-NAME-ASSUMPTION-UNA \\
& R-117-CONTEXT-SENSITIVE-CONSTRAINTS \\
& R-118-NAMESPACE-SENSITIVE-CONSTRAINTS \\
& R-122-TRADE-OFF-BETWEEN-DIMENSIONS-EXPRESSIVITY-COMPLEXITY-PREDICTABILITY \\
& R-124-DESCRIBE-DATA \\
& R-126-CUSTOMIZABLE-VALIDATION-PROCESS \\
& R-128-HUMAN-UNDERSTANDABLE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
& R-129-MACHINE-UNDERSTANDABLE-CONCRETE-SYNTAXES-FORMULATION-CONSTRAINTS \\
& R-130-CONCISE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
& R-131-OWL-AS-CONCRETE-SYNTAX-FORMULATING-CONSTRAINTS \\
& R-132-MULTIPLE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
& R-133-MULTIPLE-CONCRETE-SYNTAXES-FORMULATING-DATA \\
& R-136-MODULARITY-OF-CONSTRAINT-DEFINITIONS \\
& R-137-LEVERAGE-ON-EXISTING-TECHNOLOGIES \\
& R-138-CONSTRAINT-LANGUAGE-COMPATIBLE-WITH-SPARQL \\
& R-139-CONSTRAINT-LANGUAGE-DRIVES-USER-INTERFACE-FORM-GENERATION-AND-PRESENTATION \\
& R-140-SEPARATE-ONTOLOGIES-FROM-VALIDATION-SCHEMAS \\
& R-143-CONDITIONAL-TYPED-VALIDATION \\
& R-147-DISTRIBUTION-OF-CONSTRAINT-SCHEMAS \\
& R-148-DISTRIBUTED-VALIDATION-IN-COLLABORATIVE-ENVIRONMENTS \\
& R-149-MANAGEMENT-OF-CONSTRAINT-SCHEMA-EVOLUTION \\
& R-160-OPEN-SOURCE-CONSTRAINT-VALIDATION \\
& R-161-ACCEPTABLE-PERFORMANCE-OF-VALIDATION-ALGORITHM \\
& R-162-SPECIFICATION-PUBLICLY-AVAILABLE \\
& R-163-IMPLEMENTATION-EXISTS \\
& R-164-IMPLEMENTATION-PUBLICLY-AVAILABLE \\
& R-165-EXECUTABLE-DEMOS-EXAMPLES-USE-CASES \\
& R-168-PERFORM-BIG-DATASETS \\
& R-169-RDF-REPRESENTATION-OF-CONSTRAINT-LANGUAGE \\
& R-173-SEPARATE-CONSTRAINTS-FROM-VOCABULARIES-AND-ONTOLOGIES \\
& R-174-REUSE-CONSTRAINTS \\
& R-175-DISCOVER-CONSTRAINTS \\
& R-177-DEFINE-SEMANTICS-FOR-CONSTRAINTS \\
& R-178-ASSOCIATE-CONSTRAINTS-WITH-VOCABULARIES \\
& R-182-USE-KNOWN-CONCRETE-SYNTAX \\
\hr
\end{tabular}
\end{table}

Table~\ref{tab:RequirementsNotCoveredOWL2QL-1}
Table~\ref{tab:RequirementsNotCoveredOWL2QL-2}
Table~\ref{tab:RequirementsNotCoveredOWL2QL-3}

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL-3}
\centering
\begin{tabular}{ll}
\hr
Requirements & Covering Constraint Languages \\
\hr
R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
R-98-CHECK-VALIDITY-OF-URIS & \\
R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
R-112-EXTENSIBLE-CONSTRAINTS & \\
R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
R-119-VALIDATION-ON-NAMED-GRAPHS & \\
R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
R-123-STATE & \\
R-125-RDF-SHAPE-CHECKING & ShEx \\
R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
R-134-SPECIFY-USAGE-OF-TERMS & \\
R-135-CONSTRAINT-LEVELS & \\
R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
R-166-RDF-STREAMING-VALIDATION & \\
R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
\hr
\end{tabular}
\end{table}

@@

\begin{itemize}
	\item existential quantification to a class expression or a data range (ObjectSomeValuesFrom and DataSomeValuesFrom) in the subclass position
  \item self-restriction (ObjectHasSelf)
  \item existential quantification to an individual or a literal (ObjectHasValue, DataHasValue)
  \item enumeration of individuals and literals (ObjectOneOf, DataOneOf)
  \item universal quantification to a class expression or a data range (ObjectAllValuesFrom, DataAllValuesFrom)
  \item cardinality restrictions (ObjectMaxCardinality, ObjectMinCardinality, ObjectExactCardinality, DataMaxCardinality, DataMinCardinality, DataExactCardinality)
  \item disjunction (ObjectUnionOf, DisjointUnion, and DataUnionOf)
  \item property inclusions (SubObjectPropertyOf) involving property chains
  \item functional and inverse-functional properties (FunctionalObjectProperty, InverseFunctionalObjectProperty, and FunctionalDataProperty)
  \item transitive properties (TransitiveObjectProperty)
  \item keys (HasKey)
  \item individual equality assertions and negative property assertions (SameIndividual, NegativeObjectPropertyAssertion, NegativeDataPropertyAssertion)
\end{itemize}
